X-ray phase-contrast imaging at 100 keV on a conventional source

### 2013-11-29 hedpc.tex
Marco's significance statement, latex style fixes
    - Marco's edits to the significance statement
    - Authors correctly shown under the title
    - Fixed bold font in article body
    - Added corresponding author

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}
%\usepackage{pnastwof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Don't type in anything in the following section:
%%%%%%%%%%%%
%% For PNAS Only:
\contributor{Submitted to Proceedings
of the National Academy of Sciences of the United States of America}
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%%%%%%%%%%%%

@@

\title{X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on
a conventional source}

\author{T.~Thüring
\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}
\affil{2}{Institute for Biomedical Engineering, Swiss Federal
Institute of Technology,
Gloriastrasse 35
8092 Zurich, Switzerland}}
\author{M.~Abis
\affil{1}{}
\affil{2}{}}
\author{Z.~Wang}
\affil{1}{}
\author{C.~David}
\affil{1}{}
\author{M.~Stampanoni
\affil{1}{}
\affil{2}{}}

\author{}

@@

\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match the beam
    divergence and allow a large field of view on a short and efficient
    setup.
\end{abstract}

@@

\abbreviations{
%acronyms
CT,computed tomography;
SNR,signal-to-noise ratio;
CNR,contrast-to-noise ratio;
SEM,scanning electron microscope;
}
%% ----------------------------------------------------------------------------------------------------------------
%% The first letter of the article should be drop cap: \dropcap{}
%\dropcap{I}n this article we study the evolution of ''almost-sharp'' fronts

\section{Significance statement}
Phase sensitive X-ray imaging provides access to additional information
on the investigated samples with respect to the conventional absorption
radiography and tomography.

Here we show a grating interferometer with a new design of the optical
elements that enables a large field of view and an efficient imaging at
a target energy of~\SI{100}{\kilo\eV} on a conventional tube.

Our results demonstrate that phase contrast can be achieved at these
energies, which are relevant for many applications, ranging from medical
diagnostics to nondestructive testing or homeland security.

@@

%% Enter the largest bibliography number in the facing curly brackets
%% following \begin{thebibliography}

@@

\end{thebibliography}
\begin{thebibliography}{10}

\end{thebibliography}
\begin{thebibliography}{10}

\end{thebibliography}
\begin{thebibliography}{10}

\end{thebibliography}
\begin{thebibliography}{10}

>>>>

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{graphicx}  %figures
%\usepackage{pnastwof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Don't type in anything in the following section:
%%%%%%%%%%%%
%% For PNAS Only:
\contributor{Submitted to Proceedings
of the National Academy of Sciences of the United States of America}
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%%%%%%%%%%%%
\footlineauthor{ Corresponding author:
    M. Abis, 
    matteo.abis@psi.ch
}

@@

\title{X-ray phase-contrast imaging at 100 keV on a conventional source}

\author{T.~Thüring%
\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}%
\affil{2}{Institute for Biomedical Engineering,
    Swiss Federal Institute of Technology,
    Gloriastrasse 35,
8092 Zurich, Switzerland},%
M.~Abis%%
\affil{1}{}%
\affil{2}{},%
Z.~Wang%
\affil{1}{},%
C.~David%
\affil{1}{},%
\and%
M.~Stampanoni%
\affil{1}{}%
\affil{2}{}}

@@

\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    \SI{150}{\kilo\electronvolt} are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match the beam
    divergence and allow a large field of view on a short and efficient
    setup.
\end{abstract}

@@

\abbreviations{
%acronyms
CT, computed tomography;
SNR, signal-to-noise ratio;
CNR, contrast-to-noise ratio;
SEM, scanning electron microscope;
}
%% ----------------------------------------------------------------------------------------------------------------
%% The first letter of the article should be drop cap: \dropcap{}
%\dropcap{I}n this article we study the evolution of ''almost-sharp'' fronts

\section{Significance statement}

Phase sensitive X-ray imaging techniques provide access to new and
invaluable information compared to traditional absorption-based radiography
and tomography.

Here we show a Talbot-Lau grating interferometer based on a novel optical
design, enabling imaging at X-ray energies of~\SI{100}{\kilo\eV} and above
with a large field of view as well as a very compact and efficient geometry.

Our results demonstrate, for the first time, that phase contrast X-ray
imaging can be successfully performed at diagnostically relevant energies
using a conventional X-ray tube, with potential applications spanning from
medical imaging to nondestructive testing or homeland security.

@@

@@
